LAGOS lake depth

### 2020-02-20 figures/01_geometry.Rmd
remove junk from geometry panel, add legends

gg_scatter_shape <- st_drop_geometry(dt) %>%
  dplyr::filter(!is.na(shape_class)) %>%
  dplyr::arrange(desc(factor(shape_class, 
                        levels = c("neither", "concave", "convex")))) %>%
  ggplot() + 
  geom_point(aes(x = dist_deepest, y = dist_viscenter, color = shape_class)) +
  geom_abline(aes(intercept = 0, slope = 1)) +
  labs(color = "") +
  xlab("Deepest point distance (m)") +
  ylab("Visual center distance (m)")

gg_scatter_reservoir <- ggplot(data = st_drop_geometry(dt)) + 
  geom_point(aes(x = dist_deepest, y = dist_viscenter, color = reservoir_class)) +
  geom_abline(aes(intercept = 0, slope = 1)) +
  xlab("Deepest point distance (m)") +
  ylab("Visual center distance (m)")
```

@@

gg_slope_shape <- ggplot(data = test, 
                         aes(slope_mean, inlake_slope.y, 
                             color = shape_class)) + 
    geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  xlab("Buffer slope (mean)") +
  ylab("In-lake slope") +
  labs(color = "")

gg_slope_reservoir <- ggplot(data = test, 
                             aes(slope_mean, inlake_slope.y, 
                                 color = reservoir_class)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  xlab("Buffer slope (mean)") +
  ylab("In-lake slope") +
  labs(color = "")
```

```{r 01_geometry_grid, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=5}
theme_opts <- theme(legend.position = "none")
cowplot::plot_grid(gg_scatter_shape + 
                     labs(color = "") +
                     # theme(axis.title.x = element_blank()) +
                     theme_opts,
                   gg_scatter_reservoir + 
                     labs(color = "") +
                     theme(#axis.title.x = element_blank(), 
                           axis.title.y = element_blank()) +
                     theme_opts,
                   gg_slope_shape +
                     theme_opts,
                   gg_slope_reservoir + 
                     theme(axis.title.y = element_blank()) +
                     theme_opts, 
                   rel_widths = c(1, 0.93, 1, 1))
```

>>>>

gg_scatter_shape <- st_drop_geometry(dt) %>%
  dplyr::filter(!is.na(shape_class)) %>%
  dplyr::arrange(desc(factor(shape_class, 
                        levels = c("neither", "concave", "convex")))) %>%
  ggplot() + 
  geom_point(aes(x = dist_deepest, y = dist_viscenter, color = shape_class)) +
  # geom_abline(aes(intercept = 0, slope = 1)) +
  labs(color = "") +
  xlab("Deepest point distance (m)") +
  ylab("Visual center distance (m)")

gg_scatter_reservoir <- ggplot(data = dplyr::filter(
  st_drop_geometry(dt), !is.na(reservoir_class))) + 
  geom_point(aes(x = dist_deepest, y = dist_viscenter, color = reservoir_class)) +
  # geom_abline(aes(intercept = 0, slope = 1)) +
  xlab("Deepest point distance (m)") +
  ylab("Visual center distance (m)")
```

@@

gg_slope_shape <- ggplot(data = test, 
                         aes(slope_mean, inlake_slope.y, 
                             color = shape_class)) + 
    geom_point() +
  geom_smooth(data = dplyr::filter(test, shape_class != "neither"), 
              method = "lm", se = FALSE) +
  xlab("Buffer slope (mean)") +
  ylab("In-lake slope") +
  labs(color = "")

gg_slope_reservoir <- ggplot(data = dplyr::filter(test, !is.na(reservoir_class)), 
                             aes(slope_mean, inlake_slope.y, 
                                 color = reservoir_class)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  xlab("Buffer slope (mean)") +
  ylab("In-lake slope") +
  labs(color = "")
```

```{r 01_geometry_grid, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=5}
theme_opts <- theme(legend.position = "none")

legend_shape     <- cowplot::get_legend(gg_scatter_shape)
legend_reservoir <- cowplot::get_legend(gg_scatter_reservoir + labs(color = ""))
legend_panel     <- cowplot::plot_grid(legend_shape, legend_reservoir, 
                                       ncol = 1, 
                                       align = "hv")

cowplot::plot_grid(
  cowplot::plot_grid(gg_scatter_shape + 
                       labs(color = "") +
                       # theme(axis.title.x = element_blank()) +
                       theme_opts,
                     gg_scatter_reservoir + 
                       labs(color = "") +
                       theme(#axis.title.x = element_blank(), 
                             axis.title.y = element_blank()) +
                       theme_opts,
                     gg_slope_shape +
                       theme_opts,
                     gg_slope_reservoir + 
                       theme(axis.title.y = element_blank()) +
                       theme_opts, 
                     rel_widths = c(1, 0.93, 1, 1)), 
  legend_panel, rel_widths = c(1, 0.2)
)
```
